Sound Synthesis

### 2021-03-23 THESIS.tex
found correct image and font sizes

\usepackage[backend=biber]{biblatex}
%\usepackage{biblatex}

@@

\usepackage[no-math]{fontspec}
\defaultfontfeatures{Ligatures=TeX}
\setmainfont{Tex Gyre Termes}

@@

\bibliography{00_BIBLI,Compression}

\title{Sound Synthesis}
\author{Carlos Tarjano}

@@

@@

Once a radius $ \alpha $ is defined, alpha shapes conserve the uniqueness property, in fact tending to the convex hull when $ \alpha \to \infty $. Consider, for example, the artificially generated discrete wave in figure \ref{fig:Hulls} below, where the links between consecutive samples were deemphasized to highlight the “set of points” nature of a signal: The convex hull and a concave hull, in the form of an alpha shape with a particular value of $ \alpha $ are illustrated.

>>>>

\usepackage[backend=biber,style=authoryear]{biblatex}
\renewcommand*{\nameyeardelim}{\addcomma\space}
%\usepackage{biblatex}

@@

% \usepackage[no-math]{fontspec}
% \defaultfontfeatures{Ligatures=TeX}
% \setmainfont{Tex Gyre Termes}

\usepackage{lmodern} % Latin Modern Font

@@

\bibliography{Envelope,Compression}

\title{Sound Synthesis}
\author{Carlos Henrique Tarjano Santos}

@@

This work will make extensive use of the term sample, that, even in the context of digital signal processing, can be ambiguous. It can refer to a, usually short, sound file, as when refering to sample based instruments, or it can sometimes mean a unique point of a discrete sound wave, as when used in sample rate. We will adopt the first meaning, and prefer frame for the second; altough the usage is more comum when referring to videos, it is used in terms such as frames per second.

@@

Once a radius $ \alpha $ is defined, alpha shapes conserve the uniqueness property, in fact tending to the convex hull when $ \alpha \to \infty $. Consider, for example, the artificially generated discrete wave in figure \ref{fig:Hulls} below, where the links between consecutive samples were deemphasized to highlight the “set of points” nature of a signal: The convex hull and a concave hull, in the form of an alpha shape with a particular value of $ \alpha $ are illustrated. The successive points can be interpreted as a wave, in which case the vertical axis represents its instantaneous amplitude at each frame, the meaning of the horizontal axis. If we disconsider the lines linking each consecute point it is easy to see the image as a cloud of points in a cartesian plane, however.
